---
title: "Hello R"
author: "Elizabeth Kenreck"
date: "Data 2401"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT.

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

### Exercise 1

A datasaurus dozen has 12 data sets with 1846 rows and 3 variables.

datasaurus_dozen %\>% count(dataset) %\>% print(13)

### Exercise 2

First let's plot the data in the dino dataset:

dino_data \<- datasaurus_dozen %\>%

filter(dataset == "dino")

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Below is a plot of y vs. x for a star dataset.

```{r plot-star,  fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Then below shows the calculated correlation coefficient between x and y for the star dataset.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

When you compare the value of r for the dinoset with r for the star dataset, there is only a didfference of -0.0015.

### Exercise 4

Below is the plot of y vs. x for a circle dataset. 

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Then below shows the calculated correlation coefficient between x and y for the circle dataset.

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))

```

The differnece of r in the dino dataset and r in the circle dataset is .0038.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
